学術論文

### 2025-10-21 articles.Rmd
update

- [53] Soda, T., Toyama, A., Takeda1, M., Kunisato, Y.,  & Yamashita, Y. (in press). Reliability and Validity of the DSM-5 Level 1 Cross-Cutting Symptom Measure in Japan: Insights into General and Specific Psychiatric Symptom Assessment.

- [52] Kowal, M.,...Kunisato, Y.,...Prazeres, F. (in press). Cross-cultural data on romantic love and mate preferences from 117,293 participants across 175 countries. Scientific Data.

- [51] Buchanan, E. M.,...Kunisato, Y.,...Lewis, S.C. (in press). Measuring the semantic priming effect across many languages. Nature Human Behaviour.

@@

>>>>

- [54] Matsumoto, K., Hamatani, S., Mizuno, Y., Maeno, A., Kasai, M., Watanabe, K., Kamashita, R., Sunami, N., Ikeda, M., Nagata, S., Inoue, M., Kimura, Y., Yokoo, M., Kunisato, Y., Akasaki, Y., Nakamura, M.(in press). Self-Help Cognitive Behavioral Therapy for Gaze Anxiety in Young Adults: Protocol of a 3-Arms, Multicenter, Randomized Controlled Trial. Psychiatry and Clinical Neurosciences Reports.

@@

- [53] Buchanan, E. M.,...Kunisato, Y.,...Lewis, S.C. (2025). Measuring the semantic priming effect across many languages. Nature Human Behaviour. https://doi.org/10.1038/s41562-025-02254-x

- [52] Kowal, M.,...Kunisato, Y.,...Prazeres, F. (2025). Cross-cultural data on romantic love and mate preferences from 117,293 participants across 175 countries. Scientific Data, 12, 1103.https://doi.org/10.1038/s41597-025-05365-2

- [51] Soda, T., Toyama, A., Takeda, M., Kunisato, Y., & Yamashita, Y. (2025). Reliability and Validity of the DSM-5 Level 1 Cross-Cutting Symptom Measure in Japan: Insights into General and Specific Psychiatric Symptom Assessment. Journal of Personality Assessment, 1–13. https://doi.org/10.1080/00223891.2025.2527702
